\documentclass{article}

\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{float}
\usepackage{hyperref}

\setlength{\parindent}{1.3em}
\setlength{\parskip}{0.7em}

\begin{document}

\begin{titlepage}
   \vspace*{\stretch{1.0}}
   \begin{center}
     \Huge\textbf{wtf do i know}\\
     \vspace{5cm}
     \large\textit{Steven Deobald}\\
     \large\textit{Version 0.1}\\
     \large\textit\today\\
   \end{center}
   \vspace*{\stretch{2.0}}
\end{titlepage}

\begin{center}
  \vspace*{\stretch{1.0}}
  \Huge{certainty is failure}
  \vspace*{\stretch{1.0}}
\end{center}

\pagebreak

\begin{center}
  \vspace*{\stretch{1.0}}
  \Huge{``fuck charity''}
  \vspace*{\stretch{1.0}}
\end{center}

\pagebreak

\begin{center}
  \vspace*{\stretch{1.0}}
  \Huge{systems \hspace{1em}\textgreater\hspace{1em} statics}\\
  \vspace{3cm}
  \Huge{E: bill gates (vs. Tim Berners-Lee)}\\
  \Huge{A: nilenso is a system, nilenso \textbf{builds} systems}
  \vspace*{\stretch{1.0}}
\end{center}

\pagebreak

\begin{center}
  \vspace*{\stretch{1.0}}
  \Huge{if we are special, we shouldn't be}\\
  \vspace{3cm}
  \Huge{E: LLP agreement}\\
  \Huge{A: publish \textbf{everything}}
  \vspace*{\stretch{1.0}}
\end{center}

\pagebreak

\begin{center}
  \vspace*{\stretch{1.0}}
  \Huge{all systems are recursive, fractal}\\
  \vspace{3cm}
  \Huge{E: inside--strings/particles/dna/cells, outside--global political shift right}\\
  \Huge{A: nilenso need not control everything ; can we be a cell? a virus? ; exploit our networks? (give up on no one)}
  \vspace*{\stretch{1.0}}
\end{center}

\pagebreak

\begin{center}
  \vspace*{\stretch{1.0}}
  \Huge{open [source] ...docs, source material, designs, education, policies, hardware, business models...}\\
  \vspace{3cm}
  \Huge{E: internet, email, telephones, capitalism, science -- open always wins}\\
  \Huge{A: your fears are boring. -- anti-vaxxers, flat-earthers, and climate change deniers}
  \vspace*{\stretch{1.0}}
\end{center}

\pagebreak

\begin{center}
  \vspace*{\stretch{1.0}}
  \Huge{the future is actually pretty obvious}\\
  \vspace{3cm}
  \Huge{E: the internet, tinier + integrated devices: LIQUIDITY}\\
  \Huge{A: if a good future is not obvious to you, work on that -- and how to get there ...Starfleet?}
  \vspace*{\stretch{1.0}}
\end{center}

\pagebreak

\begin{center}
  \vspace*{\stretch{1.0}}
  \Huge{ideals are a waste of time}\\
  \vspace{3cm}
  \Huge{E: sadhana forest}\\
  \Huge{A: as in programming: ``does XYZ hurt? stop doing XYZ.'' -- note: i am not a free software idealist; it has never hurt.}
  \vspace*{\stretch{1.0}}
\end{center}

\pagebreak

\begin{center}
  \vspace*{\stretch{1.0}}
  \Huge{there is only one geography}\\
  \vspace{3cm}
  \Huge{E: this is self-evident. but: justin, sapiens, obvious globalization, etc.}\\
  \Huge{A: nothing to do here; just remember it. yay simple.org}
  \vspace*{\stretch{1.0}}
\end{center}

\pagebreak

\begin{center}
  \vspace*{\stretch{1.0}}
  \Huge{the meaning of life is selfless service}\\
  \vspace{3cm}
  \Huge{E: wat.}\\
  \Huge{A: should i even include this.}
  \vspace*{\stretch{1.0}}
\end{center}

\pagebreak

\begin{center}
  \vspace*{\stretch{1.0}}
  \Huge{fin.}
  \vspace*{\stretch{1.0}}
\end{center}


\end{document}
